Spectral partitioning identifies individual heterogeneity in the functional network topography of ventral and anterior medial prefrontal

### 2019-09-16 Manuscript.Rmd
final JTM revision

- Medial Default Network overlaps topographically with task effects such as valuation.

- Overlap at the group level could be due to variability across individuals.

- Individual subject level Default Networks were identified with Spectral Partitioning.

- Topographical organization is highly idiosyncratic, especially in frontal regions.

- Group-level overlap may be spurious and should be examined at the individual level.

@@

  Regions of human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are part of the default network (DN), and additionally are implicated in diverse cognitive functions ranging from autobiographical memory to subjective valuation. Our ability to interpret the apparent co-localization of these effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was more strongly associated with the DN than with valuation effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project). The spectral partitioning algorithm identified individual-level cortical subdivisions that were reliable across test/retest datasets and varied markedly across individuals, especially in mPFC. Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions, especially at the individual level.

Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex, spectral partitioning

@@

Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC. Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011]. Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Hassabis2007]. For other task-related effects, such as subjective valuation (i.e., greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued), the degree of overlap with DN regions is only partial and the reason for the overlap is less obvious [@Acikalin2017]. Insofar as the DN shares a subset of nodes in common with the distributed brain system that supports valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012]. As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Buckner2019; @Dinicola2019; @Spreng2012].

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that the functional topography of individual brains can be misaligned and blurred [@Fedorenko2012; @Guntupalli2018a; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains. This concern is especially pronounced in ventral mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Michalka2015; @Tobyne2018], and subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the previously reported overlap of the DN with task-related effects could, in some cases, be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of variability in the topography of the DN within mPFC and PCC across a large sample of individuals. The methods we propose for individual-level identification of DN regions have potential to benefit future investigations of the overlap between DN regions and task-related activity.

@@

  The outline of our paper is as follows. First, we defined a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level. Valuation was selected as a domain in which task-related activity patterns overlap extensively with DN regions on the medial surface, despite being segregable elsewhere [@Acikalin2017]. We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community. The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles. Test-retest analyses showed that these partitionings were similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. We found that the DN community was likely to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC. Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning). Resting-state fMRI data was acquired from the Human Connectome Project [@VanEssen2012].

@@

Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to a standardized cortical surface model (details can be found in Glasser et al., 2013). In addition, data underwent temporal denoising based on independent components [FMRIB's ICA-based X-noiseifier, FIX; @Griffanti2014; @Salimi-Khorshidi2014]. Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017]. Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of FD, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016]. Interpolation of high motion time points is performed to avoid temporal smoothing of noisy signal from head motion into the filtered signal during the bandpass procedure. After filtering and denoising, the interpolated high-motion time points were censored by deletion and each run was temporally de-meaned. The processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants. Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file). We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package [v. 1.1.2; https://igraph.org/r/; @G.2006] in R [v. 3.4.1; https://www.r-project.org/; @RTeam2018]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. All correlation values were transformed using Fisher's r to z. This produced a weighted network for each subject, in which the nodes were surface vertices and the edge weights were the correlations among them. Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, SD = `r sdPos`). We chose not to threshold the network, as the SP algorithm is well equipped to operate on complete (i.e. fully-connected) weighted graphs [@chung1997]. However, our results are unchanged if we cut all non-significant correlations from the weight matrices (uncorrected). Next, we took the exponential of the z-transformed correlations so that all weights became positive while maintaining their ordinal ranks. Ensuring that all edges were positive facilitated the construction of the graph Laplacian (see below), which requires all off-diagonal elements to have the same sign by design. We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).

@@

Where $I$ is an identity matrix of size $n$, and $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its edge weights with all other vertices). This resulted in a matrix wherein each entry was the negative normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue (traditionally called the 'Fiedler vector') to divide the network into two. The Fiedler vector consists of a set of positive and negative values and is binarized by sign to partition the network into two similarly-sized communities [@Fiedler1975]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the majority of the vertices in the DN-specific PCC parcel identified in our meta-analysis (area 7m). The completeness of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].

@@

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject. SP and Modularity have been previously found to show a tendency for underfitting and overfitting, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings. Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there were differences in overall agreement within these regions by performing a paired permutation analysis. For each individual and region we got the mean ARI with all 99 other individuals, then took the difference between regions to get an ARI difference per subject. On each of 5000 permutations each subject’s ARI difference was independently sign-flipped and the mean difference across subjects was added to a null distribution. The empirical difference in mean pairwise ARI between regions was then evaluated against this permuted distribution.

@@

We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach based on seed-based functional connectivity. Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in the PCC search space. We used the whole PCC region because it is traditionally thought to be part of the DN [@Buckner2008], it is a common area for researchers to place seeds for vertex- and volume-based connectivity analyses [@Fox2005], and it was often dominated by the DN community. We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject. We calculated three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps. Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices. These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. For 8 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days. ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals. Visual inspection showed that the community layout was well aligned across days, and so we matched the labeling of their partitionings based on the day that sufficiently covered area 7m.

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/FIG1.png")
```

@@

Within the mPFC/PCC search space, we estimated the topography of the DN for each individual. Using each individual's full time series (approximately 4800 total TRs from four 14-min scanning runs acquired over two days), we calculated the full vertex-to-vertex correlation matrix for the `r nVertices` surface vertices in the search space. We represented each individual's correlation matrix in the form of a network, with cortical surface vertices as nodes and thresholded/transformed correlation values as edge weights. We then applied the SP community detection algorithm to partition the network into two cohesive functional communities.

Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in the first two columns of Supplemental Figure 1). The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's normalized Laplacian matrix, see Methods). Since this is a data-driven approach, there is no a priori labeling for the two communities. We assigned the DN label to the community that contained the majority of the DN-specific PCC parcel from the meta-analysis (7m). We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN). In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC. The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them. This non-DN section extended posteriorly into pregenual cinglate cortex (area a24). We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results; as expected, that the area tended to be largely assigned to the DN community (Supplemental Figure 1).

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 4. A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs). B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower). The maps share considerable qualitative similarities in their gradients along the cortical surface. C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display data for each subject, and the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram displays the mean frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
# code to generate plots

@@

To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the temporal signal to noise ratio (tSNR) for each region, both before and after thresholding. We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used. A map of the mean tSNR across individuals can be found in Supplemental Figure 3. In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59). However, mean tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`). This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`). In short, mPFC had higher overall tSNR, albeit with greater variability across nodes. Applying the thresholding step allowed us to focus the analysis on vertices with high signal quality.

@@

We next explored the possible advantage of community detection relative to a more conventional seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC. We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations. We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC. The use of the whole PCC region (instead of just 7m) was meant to echo the way seed-based connectivity is often employed, relying on the group-average location of canonical DN regions. We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices. Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals. Figure 7A shows that these pairwise comparisons resembled those from the across-day comparisons above, and suggested good alignment between methods, but particularly high agreement within subject and method.

>>>>

- The topography of Default Network cortical regions varies across individuals.

- A community detection algorithm, spectral partitioning, was applied to rs-fMRI data.

- The algorithm identified individualized Default Network regions in mPFC and PCC.

- Default Network topography varied across individuals in mPFC, moreso than in PCC.

- Overlap of task effects with DN regions should be assessed at the individual level.

@@

  Regions of human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are part of the default network (DN), and additionally are implicated in diverse cognitive functions ranging from autobiographical memory to subjective valuation. Our ability to interpret the apparent co-localization of task-related effects with DN-regions is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was more strongly associated with the DN than with valuation effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project). The spectral partitioning algorithm identified individual-level cortical subdivisions that varied markedly across individuals, especially in mPFC, and were reliable across test/retest datasets. Our results point toward new strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions at the individual level.

Keywords: functional connectivity, default network, network neuroscience, medial prefrontal cortex, spectral partitioning

@@

Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral and anterior mPFC and in PCC. Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011]. Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Buckner2007; @Hassabis2007]. For other task-related effects, such as subjective valuation (i.e., greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued), the degree of overlap with DN regions is only partial and the reason for the overlap is less obvious [@Acikalin2017]. Insofar as the DN shares a subset of nodes in common with the distributed brain systems that support valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012]. As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Buckner2019; @Dinicola2019; @Spreng2012].

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that the functional topography of individual brains can be misaligned and blurred [@Fedorenko2012; @Guntupalli2018a; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains. This concern is especially pronounced in ventral mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Michalka2015; @Tobyne2018], and subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the apparent overlap of the DN with task-related effects might, in some cases, be attributable to low effective spatial resolution, and that the organization of mPFC and PCC might be better understood at the individual level. An important first step in investigating this possibility, and the goal of the present paper, is to quantify the degree of variability in the topography of the DN within mPFC and PCC across a large sample of individuals.

@@

  The outline of our paper is as follows. First, we defined a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level. Valuation was selected as an example of a cognitive domain in which group-average activity patterns overlap extensively with DN regions on the medial surface, despite being segregable elsewhere [@Acikalin2017]. We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community. The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles. Test-retest analyses showed that these partitionings were similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. We observed a trend for the DN community to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC. Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.

@@

All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning). Resting-state fMRI data were obtained from the Human Connectome Project [@VanEssen2012].

@@

Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to a standardized cortical surface model (details can be found in Glasser et al., 2013). In addition, data underwent temporal denoising based on independent components [FMRIB's ICA-based X-noiseifier, FIX; @Griffanti2014; @Salimi-Khorshidi2014]. Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017]. Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of FD, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016]. Interpolation of high motion time points was performed to avoid temporal smoothing of noisy signal from head motion into the filtered signal during the bandpass procedure. After filtering and denoising, the interpolated high-motion time points were censored by deletion and each run was temporally de-meaned. The processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants. Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file). We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package [v. 1.1.2; https://igraph.org/r/; @G.2006] in R [v. 3.4.1; https://www.r-project.org/; @RTeam2018]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. All correlation values were transformed using Fisher's r to z. This produced a weighted network for each subject, in which the nodes were surface vertices and the edge weights were the correlations among them. Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, SD = `r sdPos`). We chose not to threshold the network, as the SP algorithm is well equipped to operate on complete (i.e. fully-connected) weighted graphs [@chung1997]. However, our results were unchanged if we retained only significant correlations (*p* < 0.05, uncorrected) in the weight matrices. Next, we took the exponential of the z-transformed correlations so that all weights became positive while maintaining their ordinal ranks. Ensuring that all edges were positive facilitated the construction of the graph Laplacian (see below), which requires all off-diagonal elements to have the same sign by design. We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Section 2.7 for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).

@@

where $I$ is an identity matrix of size $n$, and $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its edge weights with all other vertices). This resulted in a matrix wherein each entry was the negative normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue (traditionally called the 'Fiedler vector') to divide the network into two. The Fiedler vector consists of a set of positive and negative values and is binarized by sign to partition the network into two similar-sized communities [@Fiedler1975]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the majority of the vertices in the DN-specific PCC parcel identified in our meta-analysis (area 7m). The completeness of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].

@@

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity maximization per subject. SP and modularity maximization have been previously found to show a tendency toward underfitting and overfitting, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings. Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there were differences in overall agreement within these regions by performing a paired permutation analysis. For each individual and region we took the mean ARI with all 99 other individuals, then took the difference between regions to get an ARI difference per subject. On each of 5000 permutations each subject’s ARI difference was independently sign-flipped and the group mean difference was added to a null distribution. The unpermuted group mean difference was then evaluated against this permuted distribution.

@@

We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach based on seed-based functional connectivity. Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in the PCC search space. We used the whole PCC region because it is traditionally thought to be a prominent node of the DN [@Buckner2008], and is a common area for researchers to place seeds for vertex- and volume-based connectivity analyses [e.g. @Fox2005]. We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject. We calculated three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps. Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices. These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. For 8 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and our community labeling scheme for the Fiedler vector produced a sign mismatch across days. ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals. Visual inspection showed that the community layout was well aligned across days, and so we matched the labeling of their partitionings based on the day that sufficiently covered area 7m.

@@

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Meta-analysis results. A: Proportion of times each ROI was reported in the valuation and DN literatures. B: Regions identified in permutation-based chi-squared tests contrasting the two literatures. Area 25 (in red) initially appeared to be associated with valuation, but was not interpreted because the effect was found to reflect carryover from subcortical foci centered in ventral striatum (see text for details). Areas in blue represent the remainder of the search space."}
# brain images were produced using the HCP wb_view. 
# see the function HCPOut for details on how they were transferred from R to CIFTI
include_graphics("./Images/FIG1.png")
```

@@

Within the mPFC/PCC search space, we estimated the topography of the DN for each individual. Using each individual's full time series (approximately 4800 total TRs from four 14-min scanning runs acquired over two days), we calculated the full vertex-to-vertex correlation matrix for the `r nVertices` surface vertices in the search space. We represented each individual's correlation matrix in the form of a network, with cortical surface vertices as nodes and transformed correlation values as edge weights. We then applied the SP community detection algorithm to partition the network into two cohesive functional communities.

Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in the first two columns of Supplemental Figure 1). The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's normalized Laplacian matrix, see Methods). Since this is a data-driven approach, there is no a priori labeling for the two communities. We assigned the DN label to the community that contained the majority of the DN-specific PCC parcel from the meta-analysis (7m). We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN). In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC. The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them. This non-DN section extended posteriorly into pregenual cingulate cortex (area a24). We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results; as expected, that area tended to be largely assigned to the DN community (Supplemental Figure 1).

@@

``` {r Variability per subject: Fiedler vector vs prop. DN plot (Fig 4), fig.align = "center", fig.width = 3, fig.height = 3, fig.cap = "Figure 4. A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs). B: Proportion of times each vertex was affiliated with the DN community across windows in one example subject (upper), and the continuous Fiedler vector map for the same subject using their full time series (lower). C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations. Grey lines display data for each subject, and the black line shows the fit from a mixed-effects logistic regression. Dashed red lines indicate the mean FV value at which maps were thresholded. The histogram displays the mean frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
# code to generate plots

@@

To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the temporal signal to noise ratio (tSNR) for each region, both before and after thresholding. We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used. A map of the mean tSNR across individuals can be found in Supplemental Figure 3. In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59). However, mean tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`). This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC increased only slightly (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`). In short, mPFC had higher overall tSNR, albeit with greater variability across nodes. Applying the thresholding step focused the analysis on vertices with high signal quality.

@@

We next explored the possible advantage of community detection relative to a more conventional seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC. We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations. We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC. The use of the whole PCC region (instead of just 7m) was meant to represent a typical approach to seed-based connectivity that relies on the group-average location of canonical DN regions. We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices. Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals. Figure 7A shows that these pairwise comparisons resembled those from the across-day comparisons above, and suggested good alignment between methods, but particularly high agreement within subject and method.
